An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-12 ex3/paper/paper.tex
Integrated total results into adv comparison

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_comparison/adv_comparison_17.pdf}
\caption{Attack success ratios per attack family. Depicted are flow detection accuracies for adversarial flows and for unmodified flows.}
\label{fig:adv_per_family}
\end{figure}

\begin{table}
\centering
\caption{Total flow accuracy for adversarial flows.}
\label{tab:adv_accuracies}
\begin{tabular}{lrrr} \toprule
& CW & FGSM & PGD \\ \midrule
CIC-IDS-2017 &	0.346	 & 0.445	& 0.539 \\ 
UNSW-NB15 &	0.326&	0.629	& 0.774 \\
\bottomrule
\end{tabular}
\end{table}
%It is interesting to note that for very large values of $\epsilon$ the success ratio starts to decrease again.This phenomenon might be due to numerical effects and might be preventable by a smaller learning rate.

@@

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_comparison/adv_comparison_17.pdf}
\caption{Attack success ratios for both dataset and per attack family for CIC-IDS-2017. Depicted are flow detection accuracies for adversarial flows and for unmodified flows.}
\label{fig:adv_per_family}
\end{figure}

% \begin{table}
% \centering
% \caption{Total flow accuracy for adversarial flows.}
% \label{tab:adv_accuracies}
% \begin{tabular}{lrrr} \toprule
% & CW & FGSM & PGD \\ \midrule
% CIC-IDS-2017 &	0.346	 & 0.445	& 0.539 \\ 
% UNSW-NB15 &	0.326&	0.629	& 0.774 \\
% \bottomrule
% \end{tabular}
% \end{table}
%It is interesting to note that for very large values of $\epsilon$ the success ratio starts to decrease again.This phenomenon might be due to numerical effects and might be preventable by a smaller learning rate.

@@

\begin{table}
% Evaluated using
% ./python learn.py --dataroot flows.pickle --net runs/Oct26_00-03-50_gpu/lstm_module_1284.pth --function test --batchSize 512
% ./python learn.py --dataroot flows15.pickle --net runs/Oct28_15-41-46_gpu/lstm_module_997.pth --function test --batchSize 512
% on Dec. 4th
\caption{Detection performance after adversarial training.} \label{tab:adv_training_performance}
\centering
\begin{tabular}{l r r r r} \toprule
& \multicolumn{2}{c}{CIC-IDS-17} & \multicolumn{2}{c}{UNSW-NB-15} \\
	&	Packet	&	Flow	&	Packet	&	Flow	\\	\midrule
Accuracy	&	0.991	&	0.997	&	0.994	&	0.981	\\
Precision	&	0.971	&	0.996	&	0.761	&	0.704	\\
Recall	&	0.979	&	0.992	&	0.970	&	0.824	\\
F1	&	0.975	&	0.994	&	0.853	&	0.759	\\
Youden	&	0.973	&	0.991	&	0.965	&	0.811	\\
